---
title: "Homework 5"
output: github_document
author: Na Yun Cho
---

```{r}
library(tidyverse)
```

# Problem 1
The raw data show data about homicides in 50 large U.S. cities. More specifically, the data include the proportions of homicides that did and did not result in an arrest across geographical regions and the racial disparities in arrest rates across different areas. 

# Problem 2 

```{r}
df = tibble(files = list.files(path = "./data", full.names = TRUE)) %>%
  mutate(file_contents = map(.x = files, ~read_csv(.x))) %>%
  unnest(file_contents) %>%
  pivot_longer(
    week_1 : week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>%
  mutate(files = str_replace(files, ".csv$", "")) %>%
  mutate(files = str_replace(files, "exp", "experimental"),
         files = str_replace(files, "con", "control")) %>%
  separate(files, into = c("arms_old", "id"), sep = "\\_") %>%
  separate(arms_old, into = c("dot", "data", "arm"), sep = "/") %>%
  select(arm, id, week, observations) %>%
  mutate(arm = as.factor(arm), id = as.numeric(id), week = as.numeric(week))
  
```

```{r}
plot = df %>%
  ggplot(aes(x = week, y = observations, group = interaction(id,arm), color = arm)) +
  geom_line() + labs(title = "Observations on each subject in experimental and control arms", x = "week", y = "observations")

plot
```
Comment: The plot shows that the observed values for the control group and experimental group are similar in the beginning (week 1~2). However, the observed values for the experimental group show an overall increasing trend and generally start getting bigger than the observed values for the control group from around week 2~3. As the experimental group's observed values show an increasing trend, the gap between the experimental and control group gets bigger as the weeks progress. By week 8, the gap between the two groups is the largest. The observed values for the control group are fairly consistent and stay within the bounds of -2.5 to 4. 


# Problem 3 

### Create a function
```{r}
sim_ttest = function(mu) {
  
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = 5)
  )
  
  sim_data %>%
    t.test(mu = 0, alternative = "two.sided", conf.level = 0.95) %>%
    broom::tidy() %>%
    select(estimate, p.value)
}

sim_ttest(0)
```

### Simulations 5000 times for mu = 0 
```{r}
sim_mu0 = rerun(5000, sim_ttest(0)) %>%
  bind_rows()
```

### Simulations 5000 times for mu = 1,2,3,4,5,6
```{r}
sim_mus = tibble(mu = c(1,2,3,4,5,6)) %>%
  mutate( 
    output = map(.x = mu, ~rerun(5000, sim_ttest(.x))), 
    estimate= map(output, bind_rows)) %>%
  select(mu, estimate) %>%
  unnest(estimate)
```

### Make plots

##### (1) step 1 of making plot 1
```{r}
test_power = 
  sim_mus %>%
  mutate(decision = case_when(
    p.value < 0.05 ~ "rejected", 
    p.value >= 0.05 ~ "fail to reject"
  )) %>%
  group_by(mu) %>%
  summarize(
    finaldecision = n(), 
    finalreject = sum(decision == "rejected")
  ) %>%
  mutate(
    prop_tests = map2(.x = finalreject, .y = finaldecision, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(mu, finaldecision, finalreject, tidy_tests) %>%
  unnest(tidy_tests) %>%
  select(mu, estimate, conf.low, conf.high) %>%
  rename(power = estimate)

test_power
```

##### (2) step 2 of making plot 1
```{r}
test_power %>% ggplot(aes(x = mu, y = power)) +
  geom_point() +
  geom_smooth() + 
  labs(title = "Association between Effect Size and Power", x = "true value of mu", y ="power")
```
Comment : The plot shows that greater the effect size, greater the power of a test. As the effect size increases from 1 to 6, the power of the test increases as well. When the effect size is around 4, the power of the test also reaches its maximum value of 1 and plataeus there. 

##### (3) step 1 of making plot 2
```{r}
all_null = sim_mus %>%
  group_by(mu) %>%
  summarize(
    all = mean(estimate)
  )

rejected_null = sim_mus %>%
  mutate(decision = case_when(
    p.value < 0.05 ~ "rejected", 
    p.value >= 0.95 ~ "fail to reject"
  )) %>%
  filter(decision == "rejected") %>%
  group_by(mu) %>%
  summarize(
    rejected = mean(estimate)
  )
```

##### (4) step 2 of making plot 2 
```{r}
plot_2 = 
  left_join(all_null, rejected_null, by = "mu") %>%
  pivot_longer(
    all:rejected, 
    names_to = "decision", 
    values_to = "average_mu_estimate"
  ) %>%
  ggplot(aes(x = mu, y = average_mu_estimate, color = decision)) + 
  geom_point() +
  geom_smooth() +
  labs(title = "Comparison between the true value of mu and the average of estimate value of mu", x = "True value of mu", y = "average estimate value of mu")

plot_2
```
Comment: The sample average of mu across tests for which the null is rejected is greater than the true value of mu until the true value of mu reaches 4. This makes sense because as the effect size increases, the power of the test increases as well, and when the effect size is around 4, the power of the test also reaches its maximum value of 1. 
